\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-06-26 doc/sw-system.tex
Fixed typo in A11

With an agent's confusion matrix in hand we can compute the
\emph{information} generated in any given classification. This will
depend on the confusion matrix elements (\Eref{eq:confmat}) but also on
the probability of the subject being classified containing a lens. The
quantity of interest is the mutual information between the prior and
posterior probabilities given the submitted classification $C$:
\begin{align}
\information =& H(T) - H(T;C) \notag \\ 
             =& -\pr(\LENS) \log_2 \pr(\LENS) \notag \\
              & -\pr(\NOT) \log_2 \pr(\NOT) \notag \\
              & -\pr(\LENS|C) \log_2 \pr(\LENS|C) \notag \\
              & -\pr(\NOT|C) \log_2 \pr(\NOT|C),
\end{align}
where, as above, $C$ can take the values $\saidLENS$ or $\saidNOT$. 
($H$ is the Shannon [cross] entropy function.) 
Substituting for the posterior probabilities using \Eref{eq:app:first} we get
an expression that just depends on the elements of the 
confusion matrix $\CM$ and the pre-classification subject lens
probability $\pr(\LENS) = p$:
\begin{align}
\information =    & -    p \log_2 p - (1-p) \log_2 (1-p) \notag \\
                  & - \log_2 \left[ \CM_{CL} p + \CM_{CN} (1-p) \right] \notag \\
                  & + \frac{1}{p \CM_{CL} + (1-p) \CM_{CN}} \notag \\ 
     \cdot [  p   & \CM_{CL} \left(\log_2 \CM_{CL} + \log_2 p\right) \notag \\
         + (1-p)  & \CM_{CN} \left(\log_2 \CM_{CN} + \log_2 (1-p)\right) ].
  \label{eq:app:infogain}
\end{align}
This expression has many interesting features.  If $p$ is either zero or
one, $\information(C) = 0$  regardless of the value of $C$ or the values
of the confusion matrix elements: if we know the subject's status with
certainty, additional classifications supply no new information. If we
set $p$ to be the prior probability, \Eref{eq:app:infogain} tells us how
much information is generated by classifying it all the way to $p = 1$
(which a perfect classifier, with $\CM_{LL} = \CM_{NN} = 1$, can do in
a single classification). For a prior probability of $2\times 10^{-4}$, 
12.3 bits are generated in such a ``detection.'' 
Conversely, only 0.0003 bits
are generated during the rejection of a subject with the same prior: we
are already fairly sure that each subject does not contain a lens!
Imperfect classifiers (with $\CM_{LL}$ and $\CM_{NN}$ less than 1)
generate less than these maximum amounts of information each
classification; the only classifiers that generate zero information are
those that have $\CM_{LL} = 1 - \CM_{NN}$. We might label such
classifiers as ``random'', since they are as likely to classify a
subject as a $\saidLENS$ no matter the true content of that subject.

\Eref{eq:app:infogain} suggests a useful information theoretical 
definition of the classifier skill  perceived by the agent. At a fixed
value of $p$, we can take the expectation value of the information gain
$\information$ over  the possible classifications that could be made:
\begin{align}
\langle\information\rangle   =& H(T) - \sum_C H(T;C) \pr(C) \notag \\ 
         &   =     p  \left[ \mathcal{S}(\CM_{LL}) + \mathcal{S}(1-\CM_{LL}) \right] \notag \\
         &     +(1-p) \left[ \mathcal{S}(\CM_{NN}) + \mathcal{S}(1-\CM_{NN}) \right] \notag \\
         & - \mathcal{S}\left[ p    \CM_{LL}       + (1-p)(1-\CM_{NN})     \right] \notag \\
         & - \mathcal{S}\left[ p (1-\CM_{LL})      + (1-p)   \CM_{NN}      \right] 
\end{align}
where the function $\mathcal{S}(x) = x \log_2(x)$. If we choose to
evaluate $\langle\information\rangle$ at $p = 0.5$, the result has some
useful properties. While random classifiers presented with  $p = 0.5$
subjects have $\skill = 0.0$  as expected, perfect classifiers appear to
the agents to have  $\skill = 1.0$. This suggests that  $\skill$, the
amount of information we expect to  gain when a classifier is presented
with a 50-50 subject, is a reasonable quantification of 
\emph{normalised skill}. A consequence of this choice is that the
integrated skill (over all agents' histories) should come out to be
equal to the number of subjects in the survey, when the search is
``complete'' (and all subjects are fully classified). Therefore, a
particular agent's integrated skill is a measure of that classifier's
\emph{contribution} to the lens search.

>>>>

With an agent's confusion matrix in hand we can compute the
\emph{information} generated in any given classification. This will
depend on the confusion matrix elements (\Eref{eq:confmat}) but also on
the probability of the subject being classified containing a lens. The
quantity of interest is the mutual information between the prior and
posterior probabilities given the submitted classification $C$:
\begin{align}
\information =& H(T) - H(T;C) \notag \\ 
             =& -\pr(\LENS) \log_2 \pr(\LENS) \notag \\
              & -\pr(\NOT) \log_2 \pr(\NOT) \notag \\
              & +\pr(\LENS|C) \log_2 \pr(\LENS|C) \notag \\
              & +\pr(\NOT|C) \log_2 \pr(\NOT|C),
\end{align}
where, as above, $C$ can take the values $\saidLENS$ or $\saidNOT$. 
($H$ is the Shannon [cross] entropy function.) 
Substituting for the posterior probabilities using \Eref{eq:app:first} we get
an expression that just depends on the elements of the 
confusion matrix $\CM$ and the pre-classification subject lens
probability $\pr(\LENS) = p$:
\begin{align}
\information =    & -    p \log_2 p - (1-p) \log_2 (1-p) \notag \\
                  & - \log_2 \left[ p \CM_{CL} + (1-p) \CM_{CN} \right] \notag \\
                  & + \frac{1}{p \CM_{CL} + (1-p) \CM_{CN}} \notag \\ 
     \cdot [  p   & \CM_{CL} \left(\log_2 \CM_{CL} + \log_2 p\right) \notag \\
         + (1-p)  & \CM_{CN} \left(\log_2 \CM_{CN} + \log_2 (1-p)\right) ].
  \label{eq:app:infogain}
\end{align}
This expression has many interesting features.  If $p$ is either zero or
one, $\information(C) = 0$  regardless of the value of $C$ or the values
of the confusion matrix elements: if we know the subject's status with
certainty, additional classifications supply no new information. If we
set $p$ to be the prior probability, \Eref{eq:app:infogain} tells us how
much information is generated by classifying it all the way to $p = 1$
(which a perfect classifier, with $\CM_{LL} = \CM_{NN} = 1$, can do in
a single classification). For a prior probability of $2\times 10^{-4}$, 
12.3 bits are generated in such a ``detection.'' 
Conversely, only 0.0003 bits
are generated during the rejection of a subject with the same prior: we
are already fairly sure that each subject does not contain a lens!
Imperfect classifiers (with $\CM_{LL}$ and $\CM_{NN}$ less than 1)
generate less than these maximum amounts of information each
classification; the only classifiers that generate zero information are
those that have $\CM_{LL} = 1 - \CM_{NN}$. We might label such
classifiers as ``random'', since they are as likely to classify a
subject as a $\saidLENS$ no matter the true content of that subject.

\Eref{eq:app:infogain} suggests a useful information theoretical 
definition of the classifier skill  perceived by the agent. At a fixed
value of $p$, we can take the expectation value of the information gain
$\information$ over  the possible classifications that could be made:
\begin{align}
\langle\information\rangle   =& H(T) - \sum_C H(T;C) \pr(C) \notag \\ 
         &   =     p  \left[ \mathcal{S}(\CM_{LL}) + \mathcal{S}(1-\CM_{LL}) \right] \notag \\
         &     +(1-p) \left[ \mathcal{S}(\CM_{NN}) + \mathcal{S}(1-\CM_{NN}) \right] \notag \\
         & - \mathcal{S}\left[ p    \CM_{LL}       + (1-p)(1-\CM_{NN})     \right] \notag \\
         & - \mathcal{S}\left[ p (1-\CM_{LL})      + (1-p)   \CM_{NN}      \right] 
\end{align}
where the function $\mathcal{S}(x) = x \log_2(x)$. If we choose to
evaluate $\langle\information\rangle$ at $p = 0.5$, the result has some
useful properties. While random classifiers presented with  $p = 0.5$
subjects have $\skill = 0.0$  as expected, perfect classifiers appear to
the agents to have  $\skill = 1.0$. This suggests that  $\skill$, the
amount of information we expect to  gain when a classifier is presented
with a 50-50 subject, is a reasonable quantification of 
\emph{normalised skill}. A consequence of this choice is that the
integrated skill (over all agents' histories) should come out to be
approximately 
equal to the number of subjects in the survey, when the search is
``complete'' (and all subjects are fully classified). Therefore, a
particular agent's integrated skill is a reasonable 
measure of that classifier's
\emph{contribution} to the lens search.
